Quality Definitions of Qualities

### 2019-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added some more definitions to robustness, performance, maintainability, reusability, portability

\subsection{Robustness}
The degree to which a system or component can function correctly in the presence of invalid inputs or stressful environmental conditions \cite{IEEEStdGlossarySET1990}.
The quality can be further informally refined as the ability of a software to keep an acceptable behavior, expressed in terms of robustness requirements, in spite of exceptional or unforeseen execution conditions (such as the unavailability of system resources, communication failures, invalid or stressful inputs, etc.) \cite{fernandez2005model}.

\subsection{Performance}

The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed, accuracy, or memory usage
\cite{IEEEStdGlossarySET1990}.  Performance considerations can make
certification challenging, since QA becomes more difficult for more complex
code.  However, as Roache~\cite[p.~355]{Roache1998} points out, using simpler
algorithms and reducing the number of options in general purpose code, is not
always a practical option.

@@

\subsection{Maintainability}

The ease with which a software system or component can be modified to correct faults, improve performance or other attributes, or adapt to a changed environment \cite{IEEEStdGlossarySET1990}. ISO/IEC 25010 refers to maintainability as the degree of effectiveness and efficiency with which a product or system can be modified by the intended maintainers \cite{ISO/IEC25010}.
Maintainability is necessary in scientific software, since change, through iteration, experimentation and exploration, is inevitable.  Models of physical phenomena and numerical techniques necessarily evolve over time~\cite{CarverEtAl2007, SegalAndMorris2008}.  Proper documentation, designed with change in mind, can greatly assist with change management.  QA activities need to take the need for creativity into account, while not smothering
it~\cite[p.~352]{Roache1998}.

\subsection{Reusability}

The degree to which a software module or other work product can be used in more than one software system \cite{IEEEStdGlossarySET1990}. Reusability provides support for the quality of reliability, since reliability
is improved by reusing trusted components~\cite{Dubois2005}.  (Care must still
be taken with reusing trusted components, since blind reuse in a new context can lead to errors, as dramatically shown in the Ariane 5 disaster~\cite[p.~37--38]{OliveiraAndStewart2006}.)  The odds of reuse are improved when it is considered right from the start.

\subsection{Portability}

The ease with which a system or component can be transferred from one hardware or software environment to another \cite{IEEEStdGlossarySET1990}. An application is portable across a class of environments to the degree that the effort required to transport and adapt it to a new environment in the class is less than the effort of redevelopment \cite{mooney1990strategies}.

>>>>

\subsection{Robustness}
\begin{defn}
The degree to which a system or component can function correctly in the presence of invalid inputs or stressful environmental conditions \cite{IEEEStdGlossarySET1990}.\\
\end{defn}
\begin{defn}
The quality can be further informally refined as the ability of a software to keep an acceptable behavior, expressed in terms of robustness requirements, in spite of exceptional or unforeseen execution conditions (such as the unavailability of system resources, communication failures, invalid or stressful inputs, etc.) \cite{fernandez2005model}.\\
\end{defn}
\begin{defn}
Code possesses the characteristic of robustness to the extent that it can continue to perform despite some violation of the assumptions in its specification \cite{boehm2007software}.
\end{defn}

\subsection{Performance}
\begin{defn}
The degree to which a system or component accomplishes its designated functions within given constraints, such as speed, accuracy, or memory usage \cite{IEEEStdGlossarySET1990}.\\
\end{defn}
\begin{defn}
How well or how rapidly the system must perform specific functions. Performance requirements encompass speed (database response times, for instance), throughput ( transactions per second), capacity (con-current usage loads), and timing (hard real-time demands) \cite{wiegers2003softreq}.
\end{defn}

@@

\subsection{Maintainability}
\begin{defn}
The ease with which a software system or component can be modified to correct faults, improve performance or other attributes, or adapt to a changed environment \cite{IEEEStdGlossarySET1990}. 
\end{defn}\
\begin{defn}
ISO/IEC 25010 refers to maintainability as the degree of effectiveness and efficiency with which a product or system can be modified by the intended maintainers \cite{ISO/IEC25010}.
\end{defn}
\begin{defn}
Effort required to locate and fix an error in a program
\cite{pressman2005software}.\\
\end{defn}
\begin{defn}
A set of attributes that bear on the effort needed to make specified modifications (which may include corrections, improvements, or adaptations of software to environmental changes and changes in the requirements and functional specifications)\cite{pfleeger2006software}.
\end{defn}

\subsection{Reusability}
\begin{defn}
The degree to which a software module or other work product can be used in more than one software system \cite{IEEEStdGlossarySET1990}. \\
\end{defn}
\begin{defn}
Extent to which a program [or parts of a program] can be reused in other applications - related to the packaging and scope of the functions that the program performs \cite{pressman2005software}.\\
\end{defn}
\begin{defn}
Code possesses the characteristic of maintainability to the extent that it facilitates updating to satisfy new requirements or to correct deficiencies \cite{boehm2007software}.
\end{defn}

\subsection{Portability}
\begin{defn}
The ease with which a system or component can be transferred from one hardware or software environment to another \cite{IEEEStdGlossarySET1990}. \\
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the effort required to transport and adapt it to a new environment in the class is less than the effort of redevelopment \cite{mooney1990strategies}.\\
\end{defn}
\begin{defn}
Effort required to transfer the program from one hardware and/or software system environment to another \cite{pressman2005software}.\\
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from one environment to another (including the organizational, hardware, of software environment)\cite{pfleeger2006software}.\\
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be operated easily and well on computer configurations other than its current one. This implies that special function features, not easily available at other facilities, are not used, that standard library functions and subroutines are selected for universal applicability, and so on \cite{boehm2007software}.
\end{defn}
